Regression Analysis of Chicago Crime Volume by Ward using Public School Data

### 2018-10-08 Paper.tex
working on paper

The crime data was contained in two datasets from 2016 and 2017.  Each record was a reported instance of a crime and contained attributes regarding location, type of crime, UCR code, and other information.  The two years of data were combined; then, crimes that occurred outside of the 2016-2017 school year were dropped.  The total number of crimes, as well as the total number of homicides, were summed by ward.  The school data was then joined to the crime data by ward to create the final dataset used in this regression analysis.\footnote{Not all of the 50 wards contained a high school.  So while 50 wards exist, this research only takes 48 into account.}\footnote{This data preprocessing was conducted using R and Python.  Scripts and data can be found in the GitHub repository for this project at \href{https://github.com/jdbul33/reimagined-parakeet}{https://github.com/jdbul33/reimagined-parakeet}.}

>>>>

The crime data was contained in two datasets from 2016 and 2017.  Each record was a reported instance of a crime and contained attributes regarding location, type of crime, UCR code, and other information.  The two years of data were combined; then, crimes that occurred outside of the 2016-2017 school year were dropped.  The total number of crimes, as well as the total number of homicides, were summed by ward.  The school data was then joined to the crime data by ward to create the final dataset used in this regression analysis.\footnote{Not all of the 50 wards contained a high school.  So while 50 wards exist, this research only takes 48 into account.}\footnote{This data preprocessing was conducted using R and Python.  Scripts and data can be found in the GitHub repository for this project at \href{https://github.com/jdbul33/reimagined-parakeet}{https://github.com/jdbul33/reimagined-parakeet}}.
